Market Simulator

### 2020-08-14 analysis/05_market_simulator.Rmd
persona Reactive element needs to be rearranged to match market simulator workbook

beta <- as.data.frame(matrix(rep(0), nrow = 38))

beta$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")

@@

>>>>

beta_persona <- as.data.frame(matrix(rep(0), nrow = 38))

beta_persona$levels = c("Persona 1", "Persona 2", "Persona 3", "Chartiy Importance", "Trust in Charity", "Donation Frequency", "Donation Amount", "Volunteer 12 Months", "Volunteer Frequence","Personal Activism", "Family Activism", "Religious Membership", "Sport or Recreational Membership", "Art, Music, or Educational Membership","Labor Union Membership", "Political Party Membership", "Environmental Organization Membership", "Professional Association", "Humanitarian or Charity Membership","Consumer Organization Membership", "Other Organization Membership", "Follow National News", "Follow International News", "News Medium","Follow Government or Public Affairs", "Travel to Developing Countries", "Political Preference", "Trust in Political Institutions", "Others Should be Charitable", "Worship Service Attendence", "Religious Importance", "Religion", "Gender", "Marital Status", "Education", "Income", "Race", "Age")

@@

    persona1 = p_beta1 # add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.
